---
title: "Demo For E-Learning Design"
author: "Ashish Gurung"
date: "2023-09-28"
output: html_document
---

```{r}
# library(irr)
library(psych)
library(ggpubr)
library(broom)
```

GOAL: Start with the simple stuff. Once you have that you can build on your findings and do more complex analysis.

What is inter-rater reliability? 
- Helps establish consistency/agreement.
- Binary Classification
Between Subjects (n=2): Cohen's Kappa
Between Subjects (n>=2): Fleiss' Kappa

```{r}
rater1 <- rbinom(400, 1, 0.50)
hist(rater1)

rater1_ <- rbinom(400, 1, 0.50)
hist(rater1)

cohen.kappa(x=cbind(rater1, rater1_))
```

```{r}
df_irr <- data.frame(rater1)
df_irr$rater2 <- df_irr$rater1

cohen.kappa(x=cbind(df_irr$rater1, df_irr$rater2))
```

```{r}
df_irr$rater3 <- df_irr$rater1
table(df_irr$rater3)
df_irr$rater3 <- df_irr$rater3 - 1
table(df_irr$rater3)
df_irr[df_irr$rater3 < 0, ]$rater3 <- 1
table(df_irr$rater3)
cohen.kappa(x=cbind(df_irr$rater1, df_irr$rater3))
```

```{r}
df_irr$rater4 <- df_irr$rater1

indices <- sample(1:400, 40, replace=FALSE)

table(df_irr$rater4)
df_irr[indices, ]$rater4 <- df_irr[indices, ]$rater4 - 1
table(df_irr$rater4)
df_irr[df_irr$rater4 < 0, ]$rater4 <- 1
table(df_irr$rater4)

cohen.kappa(x=cbind(df_irr$rater1, df_irr$rater4))
```

- What if the classification is not binary?
- What does the weighted kappa mean?
  -linear vs quadratic
  https://scikit-learn.org/stable/modules/generated/sklearn.metrics.cohen_kappa_score.html
  


Next we talk about randomization.

```{r}
mean_of_means = 0
for (i in 1:10) {
  random_sample <- sample(1:10000, 10, replace=TRUE)
  sample_mean <- mean(random_sample)
  print(sample_mean)
  mean_of_means = mean_of_means + sample_mean
}
print(mean_of_means/10)

for (i in 1:10) {
  print(mean(sample(1:10000, 100, replace=TRUE)))
}
```

Why do experiments randomize?
- Remove _____
- selection effect

DRAW a flow network as to how bias is mitigated.


Intuition Check:
Introduce factorial design.
How many factors are there in a (2 X 2) design?
How many factors are there in a (2 X 3) design?
How many factors are there in a (3 X 3) design?
How many factors are there in a (2 X 2 X 2) design?

....

let's use a classical example:
What is more important for plants: 
  water or sunlight?
  
  
                 Sunlight 
           ------------------
           |    0   |   1   |
      -----------------------
Water | 0  |  00    |  01   |
      -----------------------
      | 1  |  10    |  11   |
      -----------------------

What are the two factors here?

```{r}
col_00 <- rnorm(400, mean = 20, sd=5)
col_01 <- rnorm(400, mean = 30, sd=8)
col_10 <- rnorm(400, mean = 24, sd=6)
col_11 <- rnorm(400, mean = 50, sd=12)

df_00 <- data.frame(height = col_00, water = "no_water", sun = "no_sunlight")
df_01 <- data.frame(height = col_01, water = "no_water", sun = "sunlight")
df_10 <- data.frame(height = col_10, water = "water", sun = "no_sunlight")
df_11 <- data.frame(height = col_11, water = "water", sun = "sunlight")
df_main <- rbind(df_00, df_01, df_10, df_11)
table(df_main$water, df_main$sun)
head(df_main)

```

let us develop some intuition regarding the data

```{r}
ggboxplot(df_main, x='water', y='height', color='sun', palette = c("#00AFBB", "#E7B800"))
```

```{r}
ggboxplot(df_main, x='sun', y='height', color='water', palette = c("#00AFBB", "#E7B800"))
```

let's do a t-test for main effects:
water:
```{r}
t.test(df_main[df_main$water == 'no_water',]$height, df_main[df_main$water == 'water',]$height, alternative = "two.sided", var.equal = FALSE)
```

sunlight:
```{r}
t.test(df_main[df_main$sun == 'no_sunlight',]$height, df_main[df_main$sun == 'sunlight',]$height, alternative = "two.sided", var.equal = FALSE)
```

```{r}
two_factor_anova <- aov( height ~ sun + water, data = df_main)
summary(two_factor_anova)
```

```{r}
model.tables(two_factor_anova, type = "means", se=TRUE)
```


```{r}
tidy(TukeyHSD(two_factor_anova))
```

let's also explore sub-effects:
```{r}
two_factor_anova_interaction <- aov( height ~ sun + water + sun:water, data = df_main)
summary(two_factor_anova_interaction)
```

What does this tell us?
- The main effect of exposure to sunlight is significant 
- The main effect of exposure to water is significant 
- the effect of sunlight varies with the effect of water and vice-versa

```{r}
model.tables(two_factor_anova_interaction, type = "means", se=TRUE)
```

```{r}
tidy(TukeyHSD(two_factor_anova_interaction))
```

Bonus Points:
```{r}
# what if you knew the average height of the parent tree of the sapling
# conduct a ANCOVA

aov(height ~ sun + water + sun:water + parent_tree_height, data = df_main)
```

```{r}

```

```{r}

```

```{r}

```


